\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-27 ase20/eval.tex
[ASE] Updated Table 3
Updated Table 5
Finished filling Table 5
Slightly revised eval.tex

We developed \( \tool \) as an open source tool\footnote{The URL of the tool is
anonymized due to a double-blind review process.}, and evaluated the tool
based on the following three research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Coverage:} How much parts \( \tool \) automatically extract
the syntax and semantics from ES7 to ES10?
\item RQ2. \textbf{Check with Tests:} The syntax and semantics of the latest
version on ECMAScript (ES10) is compatible with official tests?
\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
features ready for inclusion in the next ECMAScript (ES11)?
\end{itemize}

@@

\begin{table}[t]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\vspace*{-1em}
\small
  \[
    \begin{array}{c?r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
      \text{\# Lexical prod.}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{81}}
      & \inred{\text{78.75}}\\\hline
      \text{\# Syntactic prod.}
      & \inred{\text{157}}
      & \inred{\text{167}}
      & \inred{\text{167}}
      & \inred{\text{174}}
      & \inred{\text{166.25}}\\
    \end{array}
  \]
  \[
    \begin{array}{c?r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c?}{\textbf{ES9}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-4}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \\\toprule
      \Delta \; \text{\# Lexical prod.}
      & \inred{\text{3}}
      & \inred{\text{5}}
      & \inred{\text{6}}
      & \inred{\text{4.67}}\\\hline
      \Delta \; \text{\# Syntactic prod.}
      & \inred{\text{140}}
      & \inred{\text{15}}
      & \inred{\text{8}}
      & \inred{\text{54.33}}\\
    \end{array}
  \]
\end{table}

@@

    es10-1 &
    Await &
    \makecell[l]{Passing wrong type of \\ the second argument for {\bf PromiseResolve}.} &
    \textsf{O} &
    2019-02-27 &
    2019-04-13 &
    45 days &
    \inred{XX} \\\hline

    es10-2 &
    IterationKind &
    \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
    ForIn/OfHeadEvaluation}.} &
    \textsf{X} &
    2018-02-16 &
    2020-03-25 &
    768 days &
    \inred{XX} \\\hline

    es10-3 &
    Completion &
    \makecell[l]{Not handling abrupt completion \\ in {\bf Evaluation} of {\it
    EqualityExpression}.} &
    \textsf{O} &
    2016-06-01 &
    2019-05-02 &
    1065 days &
    \inred{XX} \\\hline

@@

    es10-5 &
    ForOf &
    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
    await(var x of e)\{...\}}.} &
    \textsf{O} &
    2018-02-16 &
    2019-10-11 &
    602 days &
    \inred{XX} \\\hline

@@

    bigint-1 &
    UpdateExpression &
    \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
    \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.} &
    \textsf{X} &
    2019-11-27 &
    \inred{2019-00-00} &
    \inred{XX} days &
    \inred{XX} \\\hline

    bigint-2 &
    NumberOp &
    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
    Number::unsignedRightShift}.} &
    \textsf{X} &
    2019-11-27 &
    \inred{2019-00-00} &
    \inred{XX} days &
    \inred{XX} \\\hline

    bigint-3 &
    NumberOp &
    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
    NumberBitwiseOp}.} &
    \textsf{X} &
    2019-11-27 &
    \inred{2019-00-00} &
    \inred{XX} days &
    \inred{XX} \\\hline

    bigint-4 &
    Number &
    \makecell[l]{Not handling BigInt values in {\bf Number} constructor.} &
    \textsf{O} &
    2019-11-27 &
    \inred{2019-00-00} &
    \inred{XX} days &
    \inred{XX} \\\hline

@@

    \code{matchAll} of \code{String} &
    \inred{X} &
    \inred{X} &
    9/9 &
    5/5\\\hline

    \code{import()} &
    \inred{X} &
    \inred{X} &
    \inred{X/X} &
    \inred{X/X}\\\hline

    \code{BigInt} &
    \inred{X} &
    \inred{X} &
    258/323 &
    \inred{207}/207\\\hline

    \code{Promise.allSettled} &
    \inred{X} &
    \inred{X} &
    79/85 &
    50/50\\\hline

    \code{globalThis} &
    \inred{X} &
    \inred{X} &
    1/1 &
    1/1\\\hline

    \code{for-in} mechanics &
    \inred{X} &
    \inred{X} &
    \inred{X/X} &
    \inred{X/X}\\\hline

    Optional Chaining &
    \inred{X} &
    \inred{X} &
    72/74 &
    19/19\\\hline

    Nullish Coalescing Op. &
    \inred{X} &
    \inred{X} &
    10/10 &
    21/21\\\hline

    \code{import.meta} &
    \inred{X} &
    \inred{X} &
    \inred{X/X} &
    \inred{X/X}\\\hline

    {\bf Total} &
    \inred{X} &
    \inred{X} &
    \inred{X/X} &
    \inred{X/X}\\\hline
  \end{tabular}
\end{table}

>>>>

We developed \( \tool \) as an open source tool\footnote{The URL of the tool is
anonymized due to a double-blind review process.}, and evaluated the tool
based on the following research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Coverage:} How much parts \( \tool \) automatically extract
the syntax and semantics from ES7 to ES10?
\item RQ2. \textbf{Correctness:} Does \( \tool \) correctly extract IR-based formal
semantics from ECMAScript?
\item RQ3. \textbf{Forward Compatibility:} Is \( \tool \) applicable to language
features ready for inclusion in the next ECMAScript (ES11)?
\end{itemize}

@@

\begin{table}[t]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\vspace*{-1em}
\small
  \[
    \begin{array}{c?r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \multicolumn{1}{c}{\textbf{Average}}\\\toprule
      \text{\# Lexical productions}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{78}}
      & \inred{\text{81}}
      & \inred{\text{78.75}}\\\hline
      \text{\# Syntactic productions}
      & \inred{\text{157}}
      & \inred{\text{167}}
      & \inred{\text{167}}
      & \inred{\text{174}}
      & \inred{\text{166.25}}\\
    \end{array}
  \]
  \[
    \begin{array}{c?r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{ES7}}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c?}{\textbf{ES9}}
      & \multirow{2}{*}{\textbf{Average}}\\\cline{1-4}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{ES8}}
      & \multicolumn{1}{c|}{\textbf{ES9}}
      & \multicolumn{1}{c?}{\textbf{ES10}}
      & \\\toprule
      \Delta \; \text{\# Lexical productions}
      & \inred{\text{3}}
      & \inred{\text{5}}
      & \inred{\text{6}}
      & \inred{\text{4.67}}\\\hline
      \Delta \; \text{\# Syntactic productions}
      & \inred{\text{140}}
      & \inred{\text{15}}
      & \inred{\text{8}}
      & \inred{\text{54.33}}\\
    \end{array}
  \]
\end{table}

@@

    es10-1 &
    Await &
    \makecell[l]{Passing wrong type of \\ the second argument for {\bf PromiseResolve}.} &
    \textsf{O} &
    2019-02-27 &
    2019-04-13 &
    45 days &
    1100 \\\hline

    es10-2 &
    IterationKind &
    \makecell[l]{Missing \code{async-iterate} case \\ in the assertion of {\bf
    ForIn/OfHeadEvaluation}.} &
    \textsf{X} &
    2018-02-16 &
    2020-03-25 &
    768 days &
    1120 \\\hline

    es10-3 &
    Completion &
    \makecell[l]{Not handling abrupt completion \\ in {\bf Evaluation} of {\it
    EqualityExpression}.} &
    \textsf{O} &
    2016-06-01 &
    2019-05-02 &
    1065 days &
    1 \\\hline

@@

    es10-5 &
    ForOf &
    \makecell[l]{Two semantics of {\bf VarScopedDeclarations} \\ for \code{for
    await(var x of e)\{...\}}.} &
    \textsf{O} &
    2018-02-16 &
    2019-10-11 &
    602 days &
    0 \\\hline

@@

    bigint-1 &
    UpdateExpression &
    \makecell[l]{Using wrong variable \code{oldvalue} instead of \\
    \code{oldValue} in {\bf Evaluation} of {\it UpdateExpression}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-2 &
    NumberOp &
    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} \\ in {\bf
    Number::unsignedRightShift}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-3 &
    NumberOp &
    \makecell[l]{Using {\bf ToUint32} instead of {\bf ToInt32} \\ in {\bf
    NumberBitwiseOp}.} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    bigint-4 &
    Number &
    \makecell[l]{Not handling BigInt values in {\bf Number} constructor.} &
    \textsf{O} &
    2019-09-27 &
    2019-11-19 &
    53 days &
    \inred{XX} \\\hline

@@

    \code{matchAll} of \code{String} &
    0 &
    0 &
    9/9 &
    5/5\\\hline

    \code{import()} &
    0 &
    2 &
    22/23 &
    0/0\\\hline

    \code{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207\\\hline

    \code{Promise.allSettled} &
    0 &
    0 &
    79/85 &
    50/50\\\hline

    \code{globalThis} &
    0 &
    0 &
    1/1 &
    1/1\\\hline

    \code{for-in} mechanics &
    0 &
    0 &
    36/37 &
    0/0\\\hline

    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19\\\hline

    Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21\\\hline

    \code{import.meta} &
    0 &
    2 &
    15/15 &
    0/0\\\hline

    {\bf Total} &
    8 &
    11 &
    502/577 &
    \inred{303}/303\\\hline
  \end{tabular}
\end{table}
